Model Finding for Recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action ``Contre-exemples Utilisables par Isabelle et Coq'' (CUIC). }

### 2015-05-06 tex/main.tex
related

We described the most closely related work, by Ge and de Moura
\cite{GeDeM-CAV-09} and by Reynolds et al.\
\cite{ReyEtAl-1-RR-13,reynolds-et-al-2013}, in the introduction already.
Outside the world of SMT, model finding and counterexample generation have been
studied many times. The text below is partly adapted from Blanchette's Ph.D.\
thesis \cite{blanchette-2012-phd}.

@@

>>>>

We described the most closely related work, by Ge and de Moura
\cite{GeDeM-CAV-09} and by Reynolds et al.\
\cite{ReyEtAl-1-RR-13,reynolds-et-al-2013}, in the introduction already.
Outside the world of SMT, model finding has been
studied many times. The text below is partly adapted from Blanchette's Ph.D.\
thesis \cite{blanchette-2012-phd}.

@@

Model finding is concerned with satisfying arbitrary logical constraints. Some
tools are optimized to work with problems that correspond to total functional
programs. The QuickCheck tool for Haskell \cite{xxx} is an early example, based
on random testing. Exhaustive testing and narrowing are other popular
strategies \cite{xxx,yyy}. These tool are often much faster than model finders,
but they typically cannot cope with underspecification and nonexecutable
functions.

% others
%are Agsy for Agda \cite{xxx}, Quickcheck for Isabelle/HOL \cite{xxx}, and
% QuickChick for Coq \cite{xxx}.
